The paper on \Large \bf Blockchain Frontrunning

### 2018-08-23 frontrunning/Latex/sections/paper.tex
[frontrunning] notes from Aug 22, 2018 meeting

\subsubsection{Miners}
As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool, this is known as \textbf{transaction reordering} attack. Miners could use this power to attack any smart contract with transaction-ordering dependence vulnerability~\cite{luu2016making}.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e. TKN, presumably if this transaction goes through, it causes the price the purchased token to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN. Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer. However, miners can only front run other transactions (by reordering them) within the block they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.

@@

@@

@@

\item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}

>>>>

\subsubsection{Miners}
As mentioned above, since the Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the pending transactions sitting in the mempool, this is known as \textbf{transaction reordering} attack. Miners could use this power to attack any smart contract with transaction-ordering dependence vulnerability~\cite{luu2016making}.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e. TKN, presumably if this transaction goes through, it causes the price the purchased token to increase. So the dishonest miner can step in front of this transaction and  place his own buy order ahead of it. He would simply create his \textit{buy} of 1000 TKN and include it within a block and now he mines the previous \textit{buy} transaction of 1000 TKN. Doing so, he would receive a better rate than other network users, and can sell the assets he has received and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to send transactions in the order they prefer. However, miners can only front run other transactions (by reordering them) within the block they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order before the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}.

@@

%TODO: make pie charts for each mining pool, all non-status-ico transactions vs success-ico-transactions vs failed-ico=transactions

%TODO: describe failed/ successful transactions, what they mean!

@@

%TODO: commit and reveal : partcipation factor and no collatorization

@@

%TODO: also fixes collatorize the commit, but what about no collatorization cases but hide the participation (not really a frontrunning case)
\item{\textbf{Submarine sends}: describe. General solution similar to commit and reveal. This is to solve the participatory factor of the commit and reveal solution.}
